Species motif participation provides unique information about species risk of extinction

### 2023-05-03 manuscript/reorder_main_text.tex
Updates from Overleaf

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/roles_vs_TL.eps}
        \caption{Motif participation correlated with in-degree and trophic level, and both of these simpler role measures were also correlated with persistence. \textbf{A)} The proportion of omnivory increased with increasing degree while all other proportions decreased. \textbf{B)} The proportions of omnivory and direct competition decreased with increasing STL while the proportions of apparent competition and three-species chains increased. \textbf{C-F)} The proportion of each motif in consumer's participation vectors varied with connectance, network size, and their interaction (except for apparent competition). We show relationships for the smallest and largest values of network size (S) and connectance (C).
        }
        \label{fig:motifs_vs_TL_and_deg}
    \end{figure}

>>>>

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/roles_vs_TL.eps}
        \caption{Motif participation correlated with in-degree and trophic level, and both of these simpler role measures were also correlated with persistence. \textbf{A)} The proportion of omnivory increased with increasing degree while all other proportions decreased. \textbf{B)} The proportions of omnivory and direct competition decreased with increasing STL while the proportions of apparent competition and three-species chains increased. \textbf{C-D)} The proportion of each motif in consumer's participation vectors varied with connectance, network size, and their interaction (except for apparent competition, where the interaction was not significant). To cover the largest range of slopes, we show relationships over connectance for the smallest networks (\textbf{C}) and over network size for the most-connected networks (\textbf{D}). See also Fig. SX. }
        \label{fig:motifs_vs_TL_and_deg}
    \end{figure}
